---
title: "ggvis and reactives"
runtime: shiny
---

When using ggvis with shiny there are two ways to pass a reactive data source to ggvis.  This first method does not take advantage of ggvis integration with shiny:

```{r widget1, warning=FALSE, message=FALSE}
library(ggvis)
library(shiny)
library(dplyr)

widget_example <- function() {
  shinyApp(
    ui = fluidPage(
      responsive = FALSE,
      fluidRow(
        column(
          width = 3, 
          wellPanel(
            #control elements
            actionButton("gen_data", "Generate Data!")
          )
        ),
         
        column(
          width = 9,
          ggvisOutput("gg_vis")
        )
      )  
    ), #ui
    
    server = function(input, output, session) {
      rct_gen_data = reactive({
        input$gen_data
        
        isolate({
          data.frame(x = rnorm(100, 0, 1), y = rnorm(100, 0, 5))
        })
      })

      reactive({
        data = rct_gen_data()
        
        data %>% ggvis(x = ~x, y = ~y) %>% 
          layer_points() %>% 
          add_axis("x", title = paste0("rnorm(0,1) with mean: ", mean(data$x))) %>% 
          add_axis("y", title = paste0("rnorm(0,5) with mean: ", mean(data$y)))
      }) %>% bind_shiny("gg_vis")
    } #server
    
  ) #shinyAPP
}
```

```{r runWidget1}
widget_example()
```

This second method takes advantage of ggvis integration with shiny by passing a reactive object directly into ggvis.  However this method is still a bit restrictive with things like axis titles.

```{r widget2, warning=FALSE, message=FALSE}
library(ggvis)
library(shiny)
library(dplyr)

widget_example2 <- function() {
  shinyApp(
    ui = fluidPage(
      responsive = FALSE,
      fluidRow(
        column(
          width = 3, 
          wellPanel(
            #control elements
            actionButton("gen_data", "Generate Data!")
          )
        ),
         
        column(
          width = 9,
          ggvisOutput("gg_vis")
        )
      )  
    ), #ui
    
    server = function(input, output, session) {
      rct_gen_data = reactive({
        input$gen_data
        
        isolate({
          data.frame(x = rnorm(100, 0, 1), y = rnorm(100, 0, 5))
        })
      })
      
        rct_gen_data %>% 
        ggvis(x = ~x, y = ~y) %>% 
          layer_points() %>% 
          add_axis("x", title = "static x title") %>%
          add_axis("y", title = "static y title") %>%
          bind_shiny("gg_vis")
    } #server
    
  ) #shinyAPP
}
```

```{r runWidget2}
widget_example2()
```

ggvis is written in such a way that you can either supply it with the name of "the thing", such as a data frame, or the name of a reactive that returns "the thing".

The biggest use-case is for reactive data frames, but there are other things that can be reactive, too. Some things can't be reactive (yet), like axis and legend titles, unless you wrap the whole ggvis in a reactive.

If you wrap the whole thing in a reactive, the reactives within need to return "the thing", and not just be the name of the (inside) reactive. Clear?


Method A
--------

Method B
--------