---
title: "Intermediate Form - I"
runtime: shiny
---

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggvis)
library(shiny)
```

You'll all have to forgive us as we gave unofficial names todifferent ways of doing things, a patois of sorts. We're sure these are not the best names for this stuff, and it may have other names already, but bear with us.

Some of the layers in ggvis are combinations of `compute_` transformations and base layers of ggvis. For example, `layer_histograms` is a combination of `compute_bin` and `emit_rects` (I'll use `layer_rects` because it's easier for me).

What we have called intermediate form is the output of a `compute_` function.

Let's say you want a histogram, but you want the to flip the coordinates.

First do a `compute_bin`:

```{r}
df_intermediate <-
  mtcars %>%
  compute_bin(~mpg, binwidth = 1)

glimpse(df_intermediate)
```

For me, the intermediate form is denoted by the underscores at the end of the variable-names.

Now, we can build a regular histogram using `layer_rects`:

```{r}
df_intermediate %>%
  ggvis(x = ~xmin_, x2 = ~xmax_, y = ~count_, y2 = 0) %>%
  layer_rects()
```

Or we could build a flipped histogram:

```{r}
df_intermediate %>%
  ggvis(x = 0, x2 = ~count_, y = ~xmax_, y2 = ~xmin_) %>%
  layer_rects()
```

