---
title: "layer_images"
runtime: shiny
---

For one of the apps that we made, we wanted to be able to display images.

What we wanted was the functionality of `ggplot2::geom_raster`.

We started to use `ggvis::layer_rects`, displaying pixels as individiual rectangles, but we came across the limitation of "thousands of geometries".

```{r message=FALSE, warning=FALSE}
library(dpcDataSE) # github: SE-EEI/dpcDataSE
library(dplyr)
library(ggvis)
library(shiny)
```

We have a dataframe, `df_intensity`

```{r}
df_intensity <- dpcDataSE::conf_room_bumper$df_intensity

glimpse(df_intensity) # glimpse is a useful function
```

Let's set a few constants:

```{r}
npx <- 128
npy <- 144
```

This is inefficient:

```{r}
df_int <- df_intensity %>% 
  filter(row == 3 & col == 5) %>% # just one part of the image... 18000 pixels
  transmute(                      # new dplyr verb, combines mutate and select
    intensity = ifelse(intensity < 1, intensity, intensity * (1 - 1.e-8)),
    px = ((px - 1) %% npx) + 1, 
    py = ((py - 1) %% npy) + 1
  ) 
  
glimpse(df_int)

df_int %>%
  ggvis(x = ~px - 1, x2 = ~px, y2 = ~py, y = ~py - 1) %>%
  layer_rects(fill = ~intensity, strokeOpacity := 0) %>%
  scale_numeric("fill", domain = c(0, 1), range = c("black", "white")) %>%
  scale_numeric("y", reverse = TRUE) %>%
  hide_axis("x") %>%
  hide_axis("y") %>%
  hide_legend("fill") %>%
  set_options(height = 288, width = 256)
```

This is a bit-of-a-hack, but displays **much** quicker:

```{r}
df_img <- 
  data.frame(
    x = 0, 
    x2 = 128,
    y = 144, 
    y2 = 0,
    url = "https://se-eei.github.io/dpcDataSE/inst/img/conf_room_bumper/img_grey/conf_room-000-003-005.jpg"  
  )

gg_img <-
df_img %>%
  ggvis() %>%
  layer_images(x = ~x, x2 = ~x2, y = ~y, y2 = ~y2, url := ~url) %>%
  scale_numeric("y", reverse = TRUE) %>%
  hide_axis("x") %>%
  hide_axis("y") %>%
  set_options(
    height = 288, 
    width = 256, 
    keep_aspect = TRUE, 
    renderer = "canvas"
  ) 

gg_img
```

So why would you want to plot an image?

```{r}
slider_sample <- sliderInput(
  "nsample",
  label = "Number of samples",
  min = 1, 
  max = 100, 
  value = 30
)

slider_nbin <- sliderInput(
  "nbin",
  label = "Number of bins",
  min = 1, 
  max = 100, 
  value = 30
)
button_resample <- actionButton(
  "resample",
  label = "Resample",
  icon = icon("random")
)
```

```{r}
rct_df_sample <- reactive({
  
  input$resample
  
  if (is.null(input$nsample)) {
    index_sample <- NULL
  } else {
    index_sample <- sample(nrow(df_int), input$nsample)
  }
 
  df_int[index_sample, ]

})

rct_binwidth <- reactive({
  
  if (is.null(input$nbin)) {
    binwidth <- 1
  } else {
    binwidth <- 1/input$nbin
  }
  
})

gg_img_sample <- 
  gg_img %>%
  layer_points(
    x = ~px + 0.5,
    y = ~py + 0.5,
    fill := "red", 
    fillOpacity := 0.5,
    stroke := "red", 
    data = rct_df_sample
  )
  
gg_hist <- 
  rct_df_sample %>%
  ggvis(x = ~intensity) %>%
  layer_histograms(
    binwidth = rct_binwidth,
    fill := "red", 
    fillOpacity := 0.5,
    stroke := "red"
  ) %>%
  scale_numeric("x", domain = c(0, 1)) 
```

```{r, echo=FALSE}
slider_sample
slider_nbin
button_resample
```

```{r, echo=FALSE, fig.height=2, fig.width=3}
gg_img_sample
gg_hist
```





