---
title: "shinyBS"
runtime: shiny
---

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(ggvis)
library(shiny)
library(shinyBS)
```

This is a really neat package to augment your shiny app using bootstrap. As Alex points out, it's got a great name.

Here a demo; it's available from CRAN or GitHub, but the GitHub version has the modal windows.

```{r eval=FALSE}
devtools::install_github("ebailey78/shinyBS")
```

Here's a live demo: (http://spark.rstudio.com/johnharrison/shinyBS-Demo/)

To get this to work in the shiny-Rmd environment, I had to make an adjustment. However, this adjustment removes the dependency on the shiny backend.

```{r}
button_modal <-function (id, idModal, class = "btn", icon = NULL, label = "") 
{
  tags$div(
    align = "center", 
    tags$button(
      id = id, 
      `data-toggle` = "modal", 
      `data-target` = paste0("#", idModal), 
      class = class, 
      list(icon, label)
    )
  )
}
```

```{r}
button_modal(
  "modal_button",
  idModal = "modal_window",
  label = "Help!",
)

bsModal(
  "modal_window", 
  title = "Help!",
  trigger = "modal_button",
  includeMarkdown(file.path("help/help.md"))
)

toggleModal(session, "modal_button")
```

Note that you can write your help documentation using markdown, then just read it in.

You can also put shiny goodness in a modal window.

```{r}
select_color <- 
  selectInput(
    "color",
    label = "Fill and stroke color",
    choices = c("red", "green", "blue")
  )

rct_color <- reactive({

  if (is.null(input$color)) return("black")
  
  input$color
  
})

gg_cars <-
  mtcars %>%
  ggvis(x = ~wt, y = ~mpg) %>%
  layer_points(fill := rct_color, stroke := rct_color) 
```

```{r}
button_modal(
  "modal_button_shiny",
  idModal = "modal_window_shiny",
  label = "Moar Shiny!",
)

bsModal(
  "modal_window_shiny", 
  title = "Moar Shiny!",
  trigger = "modal_button_shiny",
  select_color,
  HTML(knit_print.ggvis(gg_cars)) # this took a *lot* of experimentation
)
```




